A Standardized Effect Size for Evaluating the Comparing the Strength of Phylogenetic Signal

### 2020-07-15 Manuscript/OldVsns/Manuscript-7.Rmd
pnas vsn

Several analytical tools have been developed to quantify phylogenetic signal in phenotypic datasets, including measures of serial independence [$\mathbf{C}$: @Abouheif1999], autocorrelation estimates [$I$: @Gittleman1990], statistical ratios of trait variation relative to what is expected given the phylogeny [$\kappa$: @Blomberg_et_al2003; @Adams2014a], and scaling parameters used in maximum likelihood fitting of the data to the phylogeny [$\lambda$: @Pagel1999], among others [e.g., @Klingenberg2010]. The statistical properties of these methods -- namely type I error rates and power -- have also been investigated to determine when phylogenetic signal can be detected and under what conditions [e.g., @Munkemuller_et_al2012; @Pavoine2012;  @DinizFilho2012; @Adams2014a; @MolinaVenegas2017; see also @Revell_et_al2008; @Revell2010]. One of the most widely used methods for characterizing phylogenetic signal in macroevolutionary studies is Pagel's $\lambda$ [@Pagel1999]. The ~~($\lambda$)~~ parameter ($\lambda$) transforms the lengths of the internal branches of the phylogeny to improve ~~a~~ THE fit of data to the phylogeny via maximum likelihood [@Pagel1999; @Freckleton_et_al2002]. Pagel's $\lambda$ ranges from $0\to1$, with larger values signifying a greater dependence of observed trait variation on the phylogeny. Pagel's $\lambda$ also has the appeal that it may be included in phylogenetic generalized least-squares regression (PGLS) to account for the degree of phylogenetic signal in comparative analyses [see @Freckleton_et_al2002]. \hfill\break

In addition to functioning as a parameter that is tuned for appropriate analysis, $\lambda$ can function as a descriptive statistic ~~to describe~~ CHARACTERIZING the relative strength of phylogenetic signal in phenotypic traits to determine the extent to which shared evolutionary history has influenced trait covariation among taxa. ~~The appeal~~ THIS DESCRIPTIVE UTILITY of $\lambda$ ~~as a descriptive statistic for evolutionary biologists~~ is ~~a~~ THE basis for interpreting "weak" versus "strong" phylogenetic signal~~,~~ (i.e., small versus large values of $\lambda$, respectively)~~,~~ in a comparative sense [e.g., @DeMeester2019; @Pintanel2019;@Su2019]. Indeed, statements regarding the strength of phylogenetic signal based on $\lambda$ are rather common in the evolutionary literature. For instance, of the 204 papers published in 2019 that estimated and reported Pagel's $\lambda$ (found from a literature survey we conducted in Google.scholar), 40% EXPLICITLY interpreted the strength of phylogenetic signal for at least one phenotypic trait. Further, because nearly half of the 1,572 $\lambda$ values reported were near 0 or 1 (Figure 1) where the biological interpretation of $\lambda$ is known, this percentage is even higher. \hfill\break

@@

Various other approaches use $\lambda$ as a parameter that can be ~~varied~~ ADJUSTED for inferences akin to sensitivity analysis. For instance, some have performed likelihood ratio tests that compare observed model fits to those obtained when $\lambda=0$ or $\lambda=1$ [@Freckleton_et_al2002; @Cooper2010; @Bose2019] or evaluated whether observed $\lambda$ differs from an expected $\lambda$, based on confidence intervals generated for the expected value [@Vandelook2019].  Qualitative comparisons of $\lambda$ estimates have also been performed for multiple traits on the same phylogenetic tree to infer whether the strength of phylogenetic signal is greater in one trait as compared to another [e.g., @Liu2019; @Bai2019]. \hfill\break

It seems intuitive to interpret the strength of phylogenetic signal based on the value of $\lambda$, as $\lambda$ is a parameter on a bounded scale ($0\to1$) for which interpretation of its extremal points are understood. Specifically, $\lambda=0$ represents no phylogenetic signal, while $\lambda=1$ is phylogenetic signal as expected under Brownian motion. However, equating values of $\lambda$ directly to the strength of phylogenetic signal presumes two important statistical properties that have not been fully explored. First, it presumes that values of $\lambda$ can be precisely estimated, as biological inferences regarding the strength of phylogenetic signal depend on high accuracy in its estimation. Therefore, understanding the precision in estimating $\lambda$ is paramount. One study [@Boettiger_et_al2012] found that estimates of Pagel's $\lambda$ displayed less variation (i.e., greater precision) when data were simulated on a large phylogeny ($N=281$) as compared to a small one ($N=13$). From this observation it was concluded that insufficient data (i.e., ~~the~~ LOW number of species) was the underlying cause of the increased variation across parameter estimates [@Boettiger_et_al2012]. Indeed, such a pattern is common with statistical estimators, as summary statistics and parameters are often more precise at greater sample sizes [@Cohen1988]. However, this conclusion also implies that the precision of $\lambda$ remains constant across its range ($\lambda = 0 \to 1$); an assumption that to date, has not been verified. Thus, despite widespread use of Pagel's [-@Pagel1999] $\lambda$ in macroevolutionary studies, at present, we lack a general understanding of the precision with which $\lambda$ can estimate levels of phylogenetic signal in phenotypic datasets. \hfill\break

Second, while estimates of $\lambda$ are within a bounded scale ($0\to1$), this does not *de-facto* imply that the estimated values of this parameter correspond to the actual strength of the underlying input signal in the data. For this to be the case, $\lambda$ must be a statistical effect size. Effect sizes are a measure of the magnitude of a statistical effect in data, represented on a common scale [@Glass1976; @Cohen1988]. Effect sizes have widespread use in many areas of the quantiative sciences, as they represent measures that may be readily summarized across datasets as in meta-analyses [@HedgesOlkin1985; @Glass1976; @Arnqvist1995], or compared among datasets [e.g., @AdamsCollyer2016; @AdamsCollyer2019b]. Unfortunatley, not all model parameters and descriptive statistics are effect sizes, and thus many summary measures must first be converted to statistics with standardized units (i.e., conversion to an effect size) for meaningful comparison [see @Rosenthal1994]. As a consequence, it follows that only if $\lambda$ is a statistical effect size can comparisons of estimates across datasets be interpretable. ~~For the case of $\lambda$, this~~ HOWEVER, THE CALCULATION AND STATISTICAL BEHAVIOR OF $\lambda$ AS AN EFFECT SIZE has not yet been explored.  \hfill\break

@@

Finally, when $\lambda$ was co-estimated with regression parameters in PGLS regression and ANOVA, the results of our simulations were quite similar. Regression parameters ($\beta$) were accurately estimated, confirming earlier findings of Revell [-@Revell2010] (see Supporting Information). However, estimates of phylogenetic signal ($\lambda$) were less precise (Figure 3; see also Supporting Information), and the spread of $\lambda_{est}$ was similar to that observed when $\lambda$ was estimated for only the dependent variable, as in Figure 2. Taken together, these findings reveal that $\lambda_{est}$ does not precisely characterize ~~observed~~ KNOWN levels of phylogenetic signal in phenotypic datasets, and that biological interpretations of the strength of phylogenetic signal based on $\lambda$ may be highly inaccurate. \hfill\break

@@

As an alternative, we described a standardized effect size ($Z$) for assessing the strength of phylogenetic signal. $Z$ expresses the magnitude of phylogenetic signal as a standard normal deviate, which is easily interpretable as the strength of phylogenetic signal relative to the mean. We applied this concept to both $\lambda$ and $\kappa$, and found that $Z_\kappa$ was a better estimate of the strength of phylogenetic signal in phenotypic data. First, $Z_\kappa$ was more precise than $Z_\lambda$, and precision was more consistent across the range of input levels of phylogenetic signal. Additionally, values of $Z_\kappa$ more accurately tracked known levels of phylogenetic signal, with changes in the actual strength of phylogenetic signal reflected in a more linear fashion by concomitant changes in the values of $Z_\kappa$ <!-- The phrasing in this sentence is a little rough. Perhaps: "Additionally, values of $Z_\kappa$ more accurately tracked changes in magnitude of known phylogenetic signal, as demonstrated by the linear relationship between $Z_\kappa and $\lambda_{in}$." -->. Thus, $Z_\kappa$ holds promise as a measure of the relative strength of phylogenetic signal that reflects the magnitude of this effect in phenotypic data. We therefore recommend that future studies interested in the strength of phylogenetic signal incorporate $Z_\kappa$ as a statistical measure of this effect. \hfill\break

@@

One important advantage of the approach advocated here is that the resulting effect sizes ($Z_\kappa$) are dimensionless, as the units of measurement cancel out during the calculation of $Z$ [@SokalRohlf2012]. Thus, $Z_\kappa$ represents the strength of phylogenetic signal on a common and comparable scale -- measured in standard deviation <!--deviations?--> -- regardless of the initial units and original scale of the phenotypic variables under investigation. This means that the strength of phylogenetic signal may be compared across datsets for continuous phenotypic traits measured in different units and scale, because those units have been standardized through their conversion to $Z_\kappa$. For example, our approach could be utilized to determine whether the strength of phylogenetic signal (say, in response to ecological differentiation) is stronger in morphological traits (linear traits: $mm$), physiological traits (metabolic rate: $\frac{O^2}{min}$), or behavioral traits (aggression: $\frac{\#{displays}}{second}$). In fact, our empirical example provided such a comparison, as SA:V is represented in $mm^{-1}$ while relative body size is a unitless ratio ($\frac{BW}{SVL}$). Additionally, our method  is capable of comparing the strength of phylogenetic signal in traits of different dimensionality, as estimates of phylogenetic signal using $\kappa$ have been generalized for multivariate data [$K_{mult}$: see @Adams2014a]. Furthermore, tests based on $\hat{Z}_{12}$ may be utilized for comparing the strength of phylogenetic signal among datasets containing a different number of species, and even for phenotypes obtained from species in different lineages, because their phylogenetic non-independence and observed variation are taken into account in the generation of the empirical sampling distribution via permutation.    \hfill\break

This study is not the first to compare $\lambda$ and $\kappa$ for their ability as statistics to measure phylogenetic signal.  Our results for $\lambda$ and $\kappa$ values are consistent with those found in the simulations performed by Münkemüller et al. [-@Munkemuller_et_al2012], but that study investigated type I error rates and statistical power, finding that $\lambda$ performed better in both regards, irrespective of species number in trees.  Although not the central focus of their study, the same tendency for variable $\lambda$ and consistent $\kappa$ at intermediate phylogenetic signal strengths was observed [see Fig. 2, @Munkemuller_et_al2012].  Recent work by Molina-Venegas and Rodríguez [-@MolinaVenegas2017] found that $\kappa$ but not $\lambda$ tended to inflate the estimate of phylogenetic signal, leading to moderate type I and type II biases, if polytomic chronograms were used.  Their work more thoroughly addressed previous observations of inflated $\kappa$ for incompletely resolved phylogenetic trees [@Davies2012; @Munkemuller_et_al2012].  An interesting question is whether an inflated $\kappa$ value leads to an inflated $Z_\kappa$ or does a tendency of a particular tree to inflate estimates of $\kappa$ also inflate the values in random permutations of a test, in which case $Z_\kappa$ is robust to polytomies?  We repeated the analyses in Figure 4, adjusting trees to have 50% collapsed nodes, per the technique of Molina-Venegas and Rodríguez [-@MolinaVenegas2017], and found results were consistent (see Supporting Information).  This confirms that any tendency of incompletely resolved trees to inflate $\kappa$ as a descriptive statistic does not inflate $Z_\kappa$ as an effect size~~, and~~. FURTHERMORE, because comparison of effect sizes in a test is a comparison of locations of observed values in their sampling distributions, ~~if the sampling distributions also~~ WHICH WOULD shift EQUALLY <!-- not sure 'equally' is the right word here. Alternatives: "similarly" "concomitantly" "correspondingly" --> because of this tendency, the $Z_{12}$ test statistic in equation 4 appears to be robust in spite of unresolved trees.  \hfill\break

Phylogenetic signal can be thought of as both an attribute to be measured in the data and a paramter that can be tuned to account for the phylogenetic non-independence among observations, for analysis of the data.  As such, $\lambda$ is appealing, as a statistic that potentially fulfills both roles.  However, the inability to estimate phylogenetic signal with $\lambda$ for data simulated with known phylogenetic signal is troublesome, and we recommend evolutionary biologists refrain from viewing it as a useful  statistic to describe the amount of phylogenetic signal in the data.  Interestingly, $\kappa$ -- when standardized to an effect size $Z_\kappa$ -- is a better statistic for measuring the amount of phylogenetic signal in data simulated with respect to known levels of $\lambda$.  Although $\lambda$ might be viewed as an important parameter for modifying the the conditional estimation of linear model coefficients with respect to phylogeny, it is neither a statistic that has meaningful comparative value as a measure of phylogenetic signal nor a statistic that lends itself well to reliable calculation of a test statistic.  By contrast, $\kappa$ has been shown here to be a reliable statistic, but only when standardized by the mean and standard deviation of its empirical sampling distribution (i.e., when converted to the effect size, $Z_\kappa$).  Because one has control over the number of permutations used in analysis, one can be assured with many permutations that the empirical sampling distribution is representative of true probability distributions [@AdamsCollyer2018b].  With low coefficients of variation for $Z_\kappa$ (Figure 4), it is difficult to imagine that a hypothesis test can improve equation 4 for efficiently comparing phylogenetic signal for different traits, different trees, or a combination of both.

>>>>

Several analytical tools have been developed to quantify phylogenetic signal in phenotypic datasets, including measures of serial independence [$\mathbf{C}$: @Abouheif1999], autocorrelation estimates [$I$: @Gittleman1990], statistical ratios of trait variation relative to what is expected given the phylogeny [$\kappa$: @Blomberg_et_al2003; @Adams2014a], and scaling parameters used in maximum likelihood fitting of the data to the phylogeny [$\lambda$: @Pagel1999], among others [e.g., @Klingenberg2010]. The statistical properties of these methods -- namely type I error rates and power -- have also been investigated to determine when phylogenetic signal can be detected and under what conditions [e.g., @Munkemuller_et_al2012; @Pavoine2012;  @DinizFilho2012; @Adams2014a; @MolinaVenegas2017; see also @Revell_et_al2008; @Revell2010]. One of the most widely used methods for characterizing phylogenetic signal in macroevolutionary studies is Pagel's $\lambda$ [@Pagel1999]. The parameter ($\lambda$) transforms the lengths of the internal branches of the phylogeny to improve the fit of data to the phylogeny via maximum likelihood [@Pagel1999; @Freckleton_et_al2002]. Pagel's $\lambda$ ranges from $0\to1$, with larger values signifying a greater dependence of observed trait variation on the phylogeny. Pagel's $\lambda$ also has the appeal that it may be included in phylogenetic generalized least-squares regression (PGLS) to account for the degree of phylogenetic signal in comparative analyses [see @Freckleton_et_al2002]. \hfill\break

In addition to functioning as a parameter that is tuned for appropriate analysis, $\lambda$ can function as a descriptive statistic characterizing the relative strength of phylogenetic signal in phenotypic traits to determine the extent to which shared evolutionary history has influenced trait covariation among taxa. The appeal of $\lambda$ as a descriptive statistic is that it serves as the basis for interpreting "weak" versus "strong" phylogenetic signal; i.e., small versus large values of $\lambda$, respectively, in a comparative sense [e.g., @DeMeester2019; @Pintanel2019;@Su2019]. Indeed, statements regarding the strength of phylogenetic signal based on $\lambda$ are rather common in the evolutionary literature. For instance, of the 204 papers published in 2019 that estimated and reported Pagel's $\lambda$ (found from a literature survey we conducted in Google.scholar), 40% explicitly interpreted the strength of phylogenetic signal for at least one phenotypic trait. Further, because nearly half of the 1,572 $\lambda$ values reported were near 0 or 1 (Figure 1) where the biological interpretation of $\lambda$ is known ($\lambda=0$ represents no phylogenetic signal, while $\lambda=1$ is phylogenetic signal as expected under Brownian motion), this percentage is even higher. \hfill\break

@@

Various other approaches use $\lambda$ as a parameter that can be adjusted for inferences that are akin to sensitivity analysis. For instance, some have performed likelihood ratio tests that compare observed model fits to those obtained when $\lambda=0$ or $\lambda=1$ [@Freckleton_et_al2002; @Cooper2010; @Bose2019] or evaluated whether observed $\lambda$ differs from an expected $\lambda$, based on confidence intervals generated for the expected value [@Vandelook2019].  Qualitative comparisons of $\lambda$ estimates have also been performed for multiple traits on the same phylogenetic tree to infer whether the strength of phylogenetic signal is greater in one trait as compared to another [e.g., @Liu2019; @Bai2019]. \hfill\break

It seems intuitive to interpret the strength of phylogenetic signal based on the value of $\lambda$, as $\lambda$ is a parameter on a bounded scale ($0\to1$) for which interpretation of its extremal points are understood. However, equating values of $\lambda$ directly to the strength of phylogenetic signal presumes two important statistical properties that have not been fully explored. First, it presumes that values of $\lambda$ can be precisely estimated, as biological inferences regarding the strength of phylogenetic signal depend on high accuracy in its estimation. Therefore, understanding the precision in estimating $\lambda$ is paramount. One study [@Boettiger_et_al2012] found that estimates of Pagel's $\lambda$ displayed less variation (i.e., greater precision) when data were simulated on a large phylogeny ($N=281$) as compared to a small one ($N=13$). From this observation it was concluded that insufficient data (i.e., low number of species) was the underlying cause of the increased variation across parameter estimates [@Boettiger_et_al2012]. Indeed, such a pattern is common with statistical estimators, as summary statistics and parameters are often more precise at greater sample sizes [@Cohen1988]. However, this conclusion also implies that the precision of $\lambda$ remains constant across its range ($\lambda = 0 \to 1$); an assumption that to date, has not been verified. Thus, despite widespread use of Pagel's [-@Pagel1999] $\lambda$ in macroevolutionary studies, at present, we lack a general understanding of the precision with which $\lambda$ can estimate levels of phylogenetic signal in phenotypic datasets. \hfill\break

Second, while estimates of $\lambda$ are within a bounded scale ($0\to1$), this does not *de-facto* imply that the estimated values of this parameter correspond to the actual strength of the underlying input signal in the data. For this to be the case, $\lambda$ must be a statistical effect size. Effect sizes are a measure of the magnitude of a statistical effect in data, represented on a common scale [@Glass1976; @Cohen1988]. Effect sizes have widespread use in many areas of the quantiative sciences, as they represent measures that may be readily summarized across datasets as in meta-analyses [@HedgesOlkin1985; @Glass1976; @Arnqvist1995], or compared among datasets [e.g., @AdamsCollyer2016; @AdamsCollyer2019b]. Unfortunately, not all model parameters and descriptive statistics are effect sizes, and thus many summary measures must first be converted to statistics with standardized units (i.e., conversion to an effect size) for meaningful comparison [see @Rosenthal1994]. As a consequence, it follows that only if $\lambda$ is a statistical effect size can comparisons of estimates across datasets be interpretable. However, the calculation and statisticl behavior of $\lambda$ as an effect size has not yet been explored.  \hfill\break

@@

When phylogenetic signal was investigated on balanced or pectinate trees, patterns in the precision of $\lambda$ were largely the same, with decreased precision at intermediate levels of phylogenetic signal (Supporting Information). Likewise, when $\lambda$ was co-estimated with regression parameters in PGLS regression and ANOVA, the results of our simulations were quite similar. Regression parameters ($\beta$) were accurately estimated, confirming earlier findings of Revell [-@Revell2010] (see Supporting Information). However, estimates of phylogenetic signal ($\lambda$) were less precise (Figure 3; see also Supporting Information), and the spread of $\lambda_{est}$ was similar to that observed when $\lambda$ was estimated for only the dependent variable, as in Figure 2. Taken together, these findings reveal that $\lambda_{est}$ does not precisely characterize known levels of phylogenetic signal in phenotypic datasets, and that biological interpretations of the strength of phylogenetic signal based on $\lambda$ may be highly inaccurate. \hfill\break

@@

As an alternative, we described a standardized effect size ($Z$) for assessing the strength of phylogenetic signal. $Z$ expresses the magnitude of phylogenetic signal as a standard normal deviate, which is easily interpretable as the strength of phylogenetic signal relative to the mean. We applied this concept to both $\lambda$ and $\kappa$, and found that $Z_\kappa$ was a better estimate of the strength of phylogenetic signal in phenotypic data. First, $Z_\kappa$ was more precise than $Z_\lambda$, and precision was more consistent across the range of input levels of phylogenetic signal. Additionally, values of $Z_\kappa$ more accurately tracked known changes in the magnitude of phylogenetic signal, as demonstrated by the linear relationship between $Z_\kappa$ and $\lambda_{in}$. Thus, $Z_\kappa$ holds promise as a measure of the relative strength of phylogenetic signal that reflects the magnitude of this effect in phenotypic data. We therefore recommend that future studies interested in the strength of phylogenetic signal incorporate $Z_\kappa$ as a statistical measure of this effect. \hfill\break

@@

One important advantage of the approach advocated here is that the resulting effect sizes ($Z_\kappa$) are dimensionless, as the units of measurement cancel out during the calculation of $Z$ [@SokalRohlf2012]. Thus, $Z_\kappa$ represents the strength of phylogenetic signal on a common and comparable scale -- measured in standard deviations -- regardless of the initial units and original scale of the phenotypic variables under investigation. This means that the strength of phylogenetic signal may be compared across datsets for continuous phenotypic traits measured in different units and scale, because those units have been standardized through their conversion to $Z_\kappa$. For example, our approach could be utilized to determine whether the strength of phylogenetic signal (say, in response to ecological differentiation) is stronger in morphological traits (linear traits: $mm$), physiological traits (metabolic rate: $\frac{O^2}{min}$), or behavioral traits (aggression: $\frac{\#{displays}}{second}$). In fact, our empirical example provided such a comparison, as SA:V is represented in $mm^{-1}$ while relative body size is a unitless ratio ($\frac{BW}{SVL}$). Additionally, our method  is capable of comparing the strength of phylogenetic signal in traits of different dimensionality, as estimates of phylogenetic signal using $\kappa$ have been generalized for multivariate data [$\kappa_{mult}$: see @Adams2014a]. Furthermore, tests based on $\hat{Z}_{12}$ may be utilized for comparing the strength of phylogenetic signal among datasets containing a different number of species, and even for phenotypes obtained from species in different lineages, because their phylogenetic non-independence and observed variation are taken into account in the generation of the empirical sampling distribution via permutation.    \hfill\break

This study is not the first to compare $\lambda$ and $\kappa$ for their ability as statistics to measure phylogenetic signal.  Our results for $\lambda$ and $\kappa$ values are consistent with those found in the simulations performed by Münkemüller et al. [-@Munkemuller_et_al2012], but that study investigated type I error rates and statistical power, finding that $\lambda$ performed better in both regards, irrespective of species number in trees.  Although not the central focus of their study, the same tendency for variable $\lambda$ and consistent $\kappa$ at intermediate phylogenetic signal strengths was observed [see Fig. 2, @Munkemuller_et_al2012].  Recent work by Molina-Venegas and Rodríguez [-@MolinaVenegas2017] found that $\kappa$ but not $\lambda$ tended to inflate the estimate of phylogenetic signal, leading to moderate type I and type II biases, if polytomic chronograms were used.  Their work more thoroughly addressed previous observations of inflated $\kappa$ for incompletely resolved phylogenetic trees [@Davies2012; @Munkemuller_et_al2012].  An interesting question is whether an inflated $\kappa$ value leads to an inflated $Z_\kappa$ or does a tendency of a particular tree to inflate estimates of $\kappa$ also inflate the values in random permutations of a test, in which case $Z_\kappa$ is robust to polytomies?  We repeated the analyses in Figure 4, adjusting trees to have 50% collapsed nodes, per the technique of Molina-Venegas and Rodríguez [-@MolinaVenegas2017], and found results were consistent (see Supporting Information).  This confirms that any tendency of incompletely resolved trees to inflate $\kappa$ as a descriptive statistic does not inflate $Z_\kappa$ as an effect size. Furthermore, because comparison of effect sizes in a test is a comparison of locations of observed values in their sampling distributions, which would shift concomitantly because of this tendency, the $Z_{12}$ test statistic in equation 4 appears to be robust in spite of unresolved trees.  \hfill\break

Phylogenetic signal can be thought of as both an attribute to be measured in the data and a parameter that can be tuned to account for the phylogenetic non-independence among observations, for analysis of the data.  As such, $\lambda$ is appealing, as a statistic that potentially fulfills both roles.  However, the inability to estimate phylogenetic signal with $\lambda$ for data simulated with known phylogenetic signal is troublesome, and we recommend evolutionary biologists refrain from viewing it as a statistic to describe the amount of phylogenetic signal in the data.  Interestingly, $\kappa$ -- when standardized to an effect size $Z_\kappa$ -- is a better statistic for measuring the amount of phylogenetic signal in data simulated with respect to known levels of $\lambda$.  Although $\lambda$ might be viewed as an important parameter for modifying the the conditional estimation of linear model coefficients with respect to phylogeny, it is neither a statistic that has meaningful comparative value as a measure of phylogenetic signal nor a statistic that lends itself well to reliable calculation of a test statistic.  By contrast, $\kappa$ has been shown here to be a reliable statistic, but only when standardized by the mean and standard deviation of its empirical sampling distribution (i.e., when converted to the effect size, $Z_\kappa$).  Because one has control over the number of permutations used in analysis, one can be assured with many permutations that the empirical sampling distribution is representative of true probability distributions [@AdamsCollyer2018b].  With low coefficients of variation for $Z_\kappa$ (Figure 4), it is difficult to imagine that a hypothesis test can improve equation 4 for efficiently comparing phylogenetic signal for different traits, different trees, or a combination of both.
